### 2025-07-19 evaluating-prediction-accuracy.qmd
20250719 - positional bias

>>>>

The association between projected and actual fantasy points tended to flatten at the higher levels of projected points, for some positions, including Running Backs, Kickers, and defensive players.
A consequence of this pattern, from the perspective of draft strategy, is that it would not make sense to draft players projected to score more than the flattening of the projected–actual curve.
For instance, drafting a highly routed Wide Receiver may be safer than drafting a highly ranked Running Back, who may be more prone to injury.
This finding was echoed by @Kartes2025 (archived at <https://perma.cc/R3WS-CAKD>) whose evaluation of the accuracy of projections by position found that:

a. Quarterbacks with preseason ranks of 6–10 showed the greatest systematic underperformance relative to their projections, suggesting that you should either draft an elite Quarterback (ranked 1–5) or wait until later rounds to draft multiple lower-ranked Quarterbacks.
a. Elite Running Backs (with preseason ranks of 1–5) showed strong underperformance (relative to projections), suggesting that you should draft Running Backs ranked 6 and below.
a. Wide Receivers showed among the more consistent and predictable patterns in projections, suggesting that it may be safer to draft a top Wide Receiver than top-ranked players at other positions.
a. Tight Ends showed relative inaccuracy of projections with limited upside concentrated among a few players, which means it is difficult, at the outset, to predict which Tight Ends will excel; based on this, @Kartes2025 suggested avoiding overpaying for mid-tier Tight Ends; to either draft a Tight End early or to wait until later rounds.

This does *not* mean that you should intentionally draft a 6th ranked Running Back instead of the top-ranked Running Back.
Instead, what it may mean is that, instead of drafting the top-ranked Running Back, you may be better off drafting the top-ranked Wide Receiver and to get a value player at Running Back in a subsequent pick.
